Intro Seminar

### 2017-03-12 doc/seminar2017.Rmd
Fixed gee coding

subCharTable <- tableone::CreateTableOne(
  vars = c("Age",
           "Sex",
           "Ethnicity",
           "BMI",
           "Waist",
           "eGFR",
           "ACR",
           "UrineCreatinine",
           "UrineMicroalbumin",
           "UrinaryCalcium",
           "UDBP",
           "Creatinine",
           "VitaminD",
           "PTH",
           "ALT",
           "Systolic",
           "Diastolic",
           "MeanArtPressure",
           "Glucose0",
           "Glucose120",
           "dmStatus",
           "SmokeCigs",
           "BirthControl"),
  strata = c("fVN"),
  data = ds,
  factorVars = c("Sex", "SmokeCigs", "BirthControl")
) %>% 
  print(nonnormal = c("Glucose0",
                      "Glucose120",
                      "ALT",
                      "UDBP",
                      "ACR")) %>% 
  knitr::kable()
```

@@

@@

gee <- ds %>%
  dplyr::mutate(
  udbpBase = ifelse(fVN == "Baseline", UDBP, NA),
  ageBase = ifelse(fVN == "Baseline", Age, NA),
  fDM = relevel(as.factor(DM), "1")
  # Ethnicity = ifelse(Ethnicity == "European", Ethnicity, "Other"),
  ) %>%
  dplyr::filter(!(fVN == "Baseline" &
                    acr_status == "Macroalbuminuria")) %>%
  dplyr::filter(!(fVN == "Baseline" & eGFR_status == "Moderate")) %>%
  dplyr::arrange(SID, fVN) %>%
  dplyr::group_by(SID) %>%
  tidyr::fill(udbpBase, ageBase) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(UDBP = UDBP/1000) %>%
  dplyr::arrange(SID, VN) %>%
  mason_gee(
  yvars = c("ACR", "eGFR"),
  xvars = "UDBP",
  covars = c("VN", "ageBase", "fDM")
  )
```

>>>>

subCharTable <- tableone::CreateTableOne(
  vars = c("Age",
           "Sex",
           "Ethnicity",
           "BMI",
           "Waist",
           "eGFR",
           "ACR",
           "UrineCreatinine",
           "UrineMicroalbumin",
           "UDBP",
           "Creatinine",
           "VitaminD",
           "PTH",
           "ALT",
           "Systolic",
           "Diastolic",
           "MeanArtPressure",
           "Glucose0",
           "Glucose120",
           "dmStatus",
           "SmokeCigs"),
  strata = c("fVN"),
  data = ds,
  factorVars = c("Sex", "SmokeCigs")
) %>% 
  print(nonnormal = c("Glucose0",
                      "Glucose120",
                      "ALT",
                      "UDBP",
                      "ACR"))
  # knitr::kable()
```

@@

```{r UDBP vs ACR time}

ds %>% 
  line_plot("")
```

@@

gee <- ds %>%
  dplyr::mutate(
  udbpBase = ifelse(fVN == "Baseline", UDBP, NA),
  ageBase = ifelse(fVN == "Baseline", Age, NA),
  fDM = relevel(as.factor(DM), "0")
  # Ethnicity = ifelse(Ethnicity == "European", Ethnicity, "Other"),
  ) %>%
  dplyr::filter(!(fVN == "Baseline" &
                    acrStatus == "Macroalbuminuria")) %>%
  dplyr::filter(!(fVN == "Baseline" & eGFRStatus == "Moderate")) %>%
  dplyr::arrange(SID, fVN) %>%
  dplyr::group_by(SID) %>%
  tidyr::fill(udbpBase, ageBase) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(UDBP = UDBP/1000) %>%
  dplyr::arrange(SID, VN) %>%

  mason::design("gee") %>% 
  mason::add_settings(
    family = stats::gaussian(),
    corstr = "ar1",
    cluster.id = "SID"
  ) %>% 
  mason::add_variables("yvars", c("ACR", "eGFR")) %>% 
  mason::add_variables("xvars", "UDBP") %>% 
  mason::add_variables("covariates", c("VN", "ageBase", "fDM")) %>% 
  mason::construct() %>% 
  mason::scrub()
```
